Who are Toronto’s Crime Victims? A Gender and Crime Type Analysis from 2014 to 2023

### 2024-09-26 paper/paper.qmd
Adjusted figures and tables for readability

#### Second Graph ####
ggplot(summary_crime, aes(x = CrimeType, y = Victims_of_Crimes, fill = Sex)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = Victims_of_Crimes),
            position = position_dodge(width = 0.9),
            vjust = -0.2,
            size = 2.5) +
  labs(x = "Crime Type", 
       y = "Number of Victims") +
  scale_y_continuous(labels = comma) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust =1))

@@

#### Third Graph ####
ggplot(summary_assault, aes(x = AssaultType, y = Victims_of_Crimes, 
                            fill = Sex)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = Victims_of_Crimes),
            position = position_dodge(width = 0.9),
            vjust = -0.2,
            size = 2.5) +
  labs(x = "Assault Type",
       y = "Number of Victims") +
  scale_y_continuous(labels = comma) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust =1))

@@

```{r}
#| label: tbl-head
#| tbl-cap: First 5 rows of cleaned data 
#| echo: false
#| warning: false
#| message: false

>>>>

#### Second Graph ####
ggplot(summary_crime, aes(x = CrimeType, y = Victims_of_Crimes, fill = Sex)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = Victims_of_Crimes),
            position = position_dodge(width = 0.95),
            vjust = -0.2,
            size = 2.5) +
  labs(x = "Crime Type", 
       y = "Number of Victims") +
  scale_y_continuous(labels = comma) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust =1))

@@

#### Third Graph ####
ggplot(summary_assault, aes(x = AssaultType, y = Victims_of_Crimes, 
                            fill = Sex)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = Victims_of_Crimes),
            position = position_dodge(width = 1.05),
            vjust = -0.2,
            size = 2.5) +
  labs(x = "Assault Type",
       y = "Number of Victims") +
  scale_y_continuous(labels = comma) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust =1))

@@

```{r}
#| label: tbl-head
#| tbl-cap: First 5 Rows of Cleaned Data 
#| echo: false
#| warning: false
#| message: false
